MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-03-22 Article.tex
Updated artifact repo

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}, \url{https://github.com/sysbio-curie/MaBoSS-env-2.0}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/sysbio-curie/gigascience24-artifact}}.

@@

The scripts, presented plots, data and instructions to reproduce the benchmarks are available on GitHub~\cite{adam_smelko_2024_10841007}.

>>>>

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}, \url{https://github.com/sysbio-curie/MaBoSS-env-2.0}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/sysbio-curie/hpcmaboss-artifact}}.

@@

The scripts, presented plots, data and instructions to reproduce the benchmarks are available on GitHub~\cite{adam_smelko_2024_10853153}.
